\LARGE{\bf{Natural variation in teosinte at the domestication locus \emph{teosinte branched1} (\emph{tb1})}}\footnotemark

### 2014-05-25 Supplement.tex
supplement
trying to get tables formatted…
edits
edits
edits
edits. having trouble with supplement, trying to figure out issues
edits
fixed so in pdf!
edits
figure out long table stuff
edits
trying to figure out long table formatting

%Note that if authors wish to submit long DNA sequence appendices as supplemental material, they should select the "DNA sequences (online-only supplemental)" option on Editorial Manager. This ensures that lengthy appendices are not built into the reviewers' PDF, but are still accessible to the reviewers.

\begin{document}

@@

% Figure S2. Gel image
%-------------------------------------------------------------------
\begin{figure*}[!t]
  \begin{center}
   \includegraphics[width=150mm]{FigS2Gel.png}
   \caption{Agarose gel image of amplification products using our primer sets. Genotypes are indicated at the top of the gel.} 
\label{FigS2Gel}
  \end{center}
\end{figure*}
%-------------------------------------------------------------------

% Figure S3. NJ Trees
%-------------------------------------------------------------------
\begin{figure*}[!t]
  \begin{center}
   \includegraphics[width=150mm]{FigS3NJtrees.pdf}
    \caption{Neighbor-Joining tree of the sequenced region in the 5? UTR (right; sequenced region 1) and the 66,169 bp upstream region (left; sequenced region 2) of \emph{tb1}. Individuals with genotype data are colored: Homozygous for the teosinte (no \emph{Hopscotch}) allele (red), homozygous for the maize (\emph{Hopscotch}) allele (blue), heterozygotes (purple). TILs (teosinte inbred lines) are colored in green, with stars indicating the 3 TILs known to have the \emph{Hopscotch} insertion. Black indicates individuals not genotyped for the \emph{Hopscotch} insertion.} 
\label{FigS3NJ}
  \end{center}
\end{figure*}
%-------------------------------------------------------------------

% Table 1
\begin{table}[htbp]
\rowcolors{2}{gray!25}{white}
  \centering
  \caption{Pairwise F\textsubscript{ST} values from sequence and \emph{Hopscotch} genotyping data}

@@

@@

    \begin{tabular}{cccc}\\\toprule
    \textbf{Accession} & \textbf{USDA Accession ID} & \textbf{Locality} & \textbf{Number Alleles Sampled} & \textbf{\emph{Hopscotch} Frequency} & \textbf{No \emph{Hopscotch} Frequency} \\

@@

    RIMME0006 & 566673 & Durango, Mexico & 2     & 0     & 1 \\
    RIMME0007 & 566680 & Guanajuato, Mexico & 2     & 0     & 1 \\
    RIMME0008 & 566681 & Michoacan, Mexico & 2     & 0     & 1 \\
    RIMME0009 & 566682 & Distrito Federal, Mexico & 2     & 0     & 1 \\
    RIMME0011 & 566685 & Mexico, Mexico & 2     & 0     & 1 \\

@@

    RIMME0017 & 699874 & Ayotlan, Mexico & 8     & 0     & 1 \\
    RIMME0021 & N/A   & El Porvenir, Mexico & 69    & 0.173913043 & 0.826086957 \\
    RIMME0026 & N/A   & Opopeo, Mexico & 42    & 0.071428571 & 0.928571429 \\
    RIMME0028 & N/A   & Puruandiro, Mexico & 28    & 0.035714286 & 0.964285714 \\
    RIMME0029 & N/A   & Ixtlan, Mexico & 35    & 0     & 1 \\
    RIMME0030 & N/A   & San Pedro, Mexico & 27    & 0     & 1 \\
    RIMME0031 & N/A   & Tenango del Aire, Mexico & 25    & 0.08  & 0.92 \\
    RIMME0032 & N/A   & Nabogame, Mexico & 24    & 0     & 1 \\
    RIMME0033 & N/A   & Puerta Encantada, Mexico & 25    & 0     & 1 \\
    RIMME0034 & N/A   & Santa Clara, Mexico & 23    & 0     & 1 \\
    RIMME0035 & N/A   & Xochimilco, Mexico & 25    & 0     & 1 \\
    RIMPA0001 & 87168 & El Salado, Mexico & 4     & 0     & 1 \\
    RIMPA0003 & 87171 & Mazatlan, Mexico & 8     & 0.125 & 0.875 \\

@@

    RIMPA0019 & 87213 & El Salado, Mexico & 2     & 0.5   & 0.5 \\
    RIMPA0029 & 87244 & N/A   & 2     & 0.5   & 0.5 \\

@@

    RIMPA0035 & 87288 & Jalisco, Mexico & 4     & 0     & 1 \\
    RIMPA0040 & 288185 & Mexico, Mexico & 4     & 0     & 1 \\
    RIMPA0042 & 288187 & Guerrero, Mexico & 4     & 0.25  & 0.75 \\
    RIMPA0043 & 288188 & Guerrero, Mexico & 4     & 0     & 1 \\
    RIMPA0045 & 288193 & Guerrero, Mexico & 4     & 0     & 1 \\

@@

    RIMPA0056 & 714153 & Breeders line & 2     & 0.5   & 0.5 \\
    RIMPA0057 & 714154 & Breeders line & 2     & 0.5   & 0.5 \\
    RIMPA0058 & N/A   & N/A   & 4     & 0.5   & 0.5 \\

@@

    RIMPA0069 & 699862 & Ixtlan, Mexico & 14    & 0.142857143 & 0.857142857 \\
    RIMPA0070 & 699863 & Benito Jaurez, Mexico & 16    & 0     & 1 \\
    RIMPA0071 & 699864 & Tuzantla, Mexico & 28    & 0     & 1 \\
    RIMPA0072 & 699865 & Tiquicheo, Mexico & 16    & 0     & 1 \\
    RIMPA0073 & 699866 & Tiquicheo, Mexico & 16    & 0.125 & 0.875 \\
    RIMPA0074 & 699867 & Huetamo, Mexico & 12    & 0     & 1 \\
    RIMPA0075 & 699868 & Huetamo, Mexico & 2     & 0     & 1 \\
    RIMPA0076 & 699869 & Huetamo, Mexico & 4     & 0     & 1 \\
    RIMPA0077 & 699870 & Caracuaro, Mexico & 2     & 0     & 1 \\
    RIMPA0078 & 699871 & Caracuaro, Mexico & 2     & 0.5   & 0.5 \\
    RIMPA0079 & 699872 & Villa Madero, Mexico & 14    & 0     & 1 \\
    RIMPA0080 & 699873 & Guachinango, Mexico & 12    & 0     & 1 \\
    RIMPA0081 & 699875 & Ameca, Mexico & 16    & 0     & 1 \\
    RIMPA0083 & 699877 & Tepoztlan, Mexico & 14    & 0     & 1 \\
    RIMPA0084 & 699878 & Tepoztlan, Mexico & 16    & 0     & 1 \\
    RIMPA0085 & 699879 & Miahuatlan, Mexico & 16    & 0     & 1 \\
    RIMPA0086 & 699880 & Miahuatlan, Mexico & 16    & 0.0625 & 0.9375 \\
    RIMPA0087 & 699881 & Tecoanapa, Mexico & 24    & 0     & 1 \\
    RIMPA0089 & 699883 & Guerrero, Mexico & 12    & 0     & 1 \\
    RIMPA0090 & 699884 & Guerrero, Mexico & 10    & 0     & 1 \\
    RIMPA0091 & 699885 & Guerrero, Mexico & 16    & 0     & 1 \\
    RIMPA0092 & 699886 & Guerrero, Mexico & 10    & 0     & 1 \\
    RIMPA0093 & 699887 & Guerrero, Mexico & 26    & 0.076923077 & 0.923076923 \\
    RIMPA0094 & 699888 & Guerrero, Mexico & 2     & 0     & 1 \\
    RIMPA0095 & 699889 & Guerrero, Mexico & 4     & 0     & 1 \\
    RIMPA0096 & 699890 & Guerrero, Mexico & 26    & 0.038461538 & 0.961538462 \\
    RIMPA0097 & 699891 & Guerrero, Mexico & 6     & 0     & 1 \\
    RIMPA0098 & 699892 & Guerrero, Mexico & 4     & 0     & 1 \\
    RIMPA0099 & 699893 & Guerrero, Mexico & 4     & 0     & 1 \\
    RIMPA0100 & 699894 & Guerrero, Mexico & 6     & 0     & 1 \\
    RIMPA0101 & 699895 & Guerrero, Mexico & 2     & 0     & 1 \\
    RIMPA0103 & 699897 & Guerrero, Mexico & 2     & 0     & 1 \\
    RIMPA0104 & 699898 & Guerrero, Mexico & 22    & 0.090909091 & 0.909090909 \\
    RIMPA0105 & 699899 & Guerrero, Mexico & 6     & 0     & 1 \\
    RIMPA0106 & 699900 & Guerrero, Mexico & 6     & 0.333333333 & 0.666666667 \\
    RIMPA0107 & 699901 & Guerrero, Mexico & 4     & 0     & 1 \\
    RIMPA0108 & 699902 & Guerrero, Mexico & 6     & 0     & 1 \\
    RIMPA0109 & 699903 & Michoacan, Mexico & 4     & 0.25  & 0.75 \\
    RIMPA0110 & 699904 & Michoacan, Mexico & 2     & 0     & 1 \\
    RIMPA0111 & 699905 & Michoacan, Mexico & 4     & 0     & 1 \\
    RIMPA0112 & 699906 & Michoacan, Mexico & 4     & 0.25  & 0.75 \\
    RIMPA0114 & 699908 & Michoacan, Mexico & 6     & 0.166666667 & 0.833333333 \\
    RIMPA0116 & 699910 & Mexico, Mexico & 2     & 0     & 1 \\
    RIMPA0117 & 699911 & Mexico, Mexico & 4     & 0     & 1 \\
    RIMPA0118 & 699912 & Mexico, Mexico & 6     & 0.166666667 & 0.833333333 \\
    RIMPA0119 & 699913 & Mexico, Mexico & 2     & 0     & 1 \\
    RIMPA0120 & 699914 & Mexico, Mexico & 1     & 1     & 0 \\
    RIMPA0121 & 699915 & Mexico, Mexico & 2     & 0     & 1 \\
    RIMPA0128 & 699922 & Mexico, Mexico & 2     & 0.5   & 0.5 \\
    RIMPA0129 & 699923 & Michoacan, Mexico & 2     & 0.5   & 0.5 \\
    RIMPA0135 & 699929 & Nayarit, Mexico & 24    & 0     & 1 \\
    RIMPA0138 & 699932 & Jalisco, Mexico & 2     & 0.5   & 0.5 \\
    RIMPA0139 & 699933 & Jalisco, Mexico & 1     & 1     & 0 \\
    RIMPA0142 & 699936 & Colima, Mexico & 18    & 0.444444444 & 0.555555556 \\
    RIMPA0144 & 699938 & Jalisco, Mexico & 2     & 1     & 0 \\
    RIMPA0145 & 699939 & Michoacan, Mexico & 1     & 1     & 0 \\
    RIMPA0147 & 699941 & Jalisco, Mexico & 1     & 1     & 0 \\
    RIMPA0155 & N/A   & Jalisco, Mexico & 73    & 0.01369863 & 0.98630137 \\
    RIMPA0156 & N/A   & Jalisco, Mexico & 20    & 0     & 1 \\
    RIMPA0157 & N/A   & Jalisco, Mexico & 58    & 0.344827586 & 0.655172414 \\
    RIMPA0158 & N/A   & Jalisco, Mexico & 64    & 0.53125 & 0.46875 \\
    RIMPA0159 & N/A   & Jalisco, Mexico & 26    & 0     & 1 \\
    RIMPA0162 & 21785 & N/A   & 4     & 0     & 1 \\\bottomrule

@@

% Table S2. Mays sampling

@@

>>>>

%Note that if authors wish to submit long DNA sequence appendices as supplemental material, they should select the "DNA sequences (online-only supplemental)" option on Editorial Manager. This ensures that lengthy appendices are not built into the reviewers' PDF, but are still accessible to the reviewers.
\documentclass[11pt]{article}
\usepackage{geometry} 
\usepackage{hyperref}
\usepackage[leftcaption]{sidecap}
\sidecaptionvpos{figure}{c} %position side caption
\usepackage{lineno}
\usepackage{lipsum}
\usepackage{indentfirst}
\usepackage{color}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage[pdftex]{graphicx}  
\usepackage{caption}
\usepackage{natbib}
\usepackage{authblk}
\usepackage[table]{xcolor} %for table line color alteration
\usepackage{subscript}
\usepackage{longtable}
\begin{document}

@@

% Figure S2. Gel image
%-------------------------------------------------------------------
\begin{figure*}[!t]
  \begin{center}
   \includegraphics[width=140mm]{FigS2Gel.png}
   \caption{Agarose gel image of amplification products using our primer sets. Genotypes are indicated at the top of the gel.} 
\label{FigS2Gel}
  \end{center}
\end{figure*}
%-------------------------------------------------------------------

% Figure S3. NJ Trees
%-------------------------------------------------------------------
\begin{figure*}[!t]
  \begin{center}
   \includegraphics[width=140mm]{FigS3NJtrees.pdf}
    \caption{Neighbor-Joining tree of the sequenced region in the 5? UTR (right; sequenced region 1) and the 66,169 bp upstream region (left; sequenced region 2) of \emph{tb1}. Individuals with genotype data are colored: Homozygous for the teosinte (no \emph{Hopscotch}) allele (red), homozygous for the maize (\emph{Hopscotch}) allele (blue), heterozygotes (purple). TILs (teosinte inbred lines) are colored in green, with stars indicating the 3 TILs known to have the \emph{Hopscotch} insertion. Black indicates individuals not genotyped for the \emph{Hopscotch} insertion.} 
\label{FigS3NJ}
  \end{center}
\end{figure*}
%-------------------------------------------------------------------

% Table S1
\begin{table}[htbp]
\rowcolors{2}{gray!25}{white}
  \centering
  \caption{Pairwise F\textsubscript{ST} values from sequence and \emph{Hopscotch} genotyping data}

@@

\setlength\LTleft{-30pt}            
\setlength\LTright{-30pt}
\begin{longtable}{ccp{5cm}cp{5cm}ccc}

@@

\hline
 \textbf{Accession} & \textbf{USDA ID} & \textbf{Locality} & \textbf{Number Alleles Sampled} & \textbf{\emph{Hopscotch} Frequency} & \textbf{No \emph{Hopscotch} Frequency} \\\toprule
\endhead
\hline

@@

    RIMME0006 & 566673 & Durango & 2	& 0 & 1 \\
    RIMME0007 & 566680 & Guanajuato & 2 & 0 & 1 \\
    RIMME0008 & 566681 & Michoacan & 2 & 0 & 1 \\
    RIMME0009 & 566682 & Distrito Federal & 2 & 0 & 1 \\
    RIMME0011 & 566685 & Mexico & 2     & 0     & 1 \\

@@

    RIMME0017 & 699874 & Ayotlan & 8     & 0     & 1 \\
    RIMME0021 & N/A   & El Porvenir & 69    & 0.17 & 0.83 \\
    RIMME0026 & N/A   & Opopeo & 42    & 0.07 & 0.93 \\
    RIMME0028 & N/A   & Puruandiro & 28    & 0.04 & 0.96 \\
    RIMME0029 & N/A   & Ixtlan & 35    & 0     & 1 \\
    RIMME0030 & N/A   & San Pedro & 27    & 0     & 1 \\
    RIMME0031 & N/A   & Tenango del Aire & 25    & 0.08  & 0.92 \\
    RIMME0032 & N/A   & Nabogame & 24    & 0     & 1 \\
    RIMME0033 & N/A   & Puerta Encantada & 25    & 0     & 1 \\
    RIMME0034 & N/A   & Santa Clara & 23    & 0     & 1 \\
    RIMME0035 & N/A   & Xochimilco & 25    & 0     & 1 \\
    RIMPA0001 & 87168 & El Salado & 4     & 0     & 1 \\
    RIMPA0003 & 87171 & Mazatlan & 8     & 0.13 & 0.87 \\

@@

    RIMPA0019 & 87213 & El Salado & 2     & 0.50   & 0.50 \\
    RIMPA0029 & 87244 & N/A   & 2     & 0.50   & 0.50 \\

@@

    RIMPA0035 & 87288 & Jalisco & 4     & 0     & 1 \\
    RIMPA0040 & 288185 & Mexico & 4     & 0     & 1 \\
    RIMPA0042 & 288187 & Guerrero & 4     & 0.25  & 0.75 \\
    RIMPA0043 & 288188 & Guerrero & 4     & 0     & 1 \\
    RIMPA0045 & 288193 & Guerrero & 4     & 0     & 1 \\

@@

    RIMPA0056 & 714153 & Breeders line & 2     & 0.50   & 0.50 \\
    RIMPA0057 & 714154 & Breeders line & 2     & 0.50   & 0.50 \\
    RIMPA0058 & N/A   & N/A   & 4     & 0.50   & 0.50 \\

@@

    RIMPA0069 & 699862 & Ixtlan & 14    & 0.142857143 & 0.857142857 \\
    RIMPA0070 & 699863 & Benito Jaurez & 16    & 0     & 1 \\
    RIMPA0071 & 699864 & Tuzantla & 28    & 0     & 1 \\
    RIMPA0072 & 699865 & Tiquicheo & 16    & 0     & 1 \\
    RIMPA0073 & 699866 & Tiquicheo & 16    & 0.125 & 0.875 \\
    RIMPA0074 & 699867 & Huetamo & 12    & 0     & 1 \\
    RIMPA0075 & 699868 & Huetamo & 2     & 0     & 1 \\
    RIMPA0076 & 699869 & Huetamo & 4     & 0     & 1 \\
    RIMPA0077 & 699870 & Caracuaro & 2     & 0     & 1 \\
    RIMPA0078 & 699871 & Caracuaro & 2     & 0.5   & 0.5 \\
    RIMPA0079 & 699872 & Villa Madero & 14    & 0     & 1 \\
    RIMPA0080 & 699873 & Guachinango & 12    & 0     & 1 \\
    RIMPA0081 & 699875 & Ameca & 16    & 0     & 1 \\
    RIMPA0083 & 699877 & Tepoztlan & 14    & 0     & 1 \\
    RIMPA0084 & 699878 & Tepoztlan & 16    & 0     & 1 \\
    RIMPA0085 & 699879 & Miahuatlan & 16    & 0     & 1 \\
    RIMPA0086 & 699880 & Miahuatlan & 16    & 0.0625 & 0.9375 \\
    RIMPA0087 & 699881 & Tecoanapa & 24    & 0     & 1 \\
    RIMPA0089 & 699883 & Guerrero & 12    & 0     & 1 \\
    RIMPA0090 & 699884 & Guerrero & 10    & 0     & 1 \\
    RIMPA0091 & 699885 & Guerrero & 16    & 0     & 1 \\
    RIMPA0092 & 699886 & Guerrero & 10    & 0     & 1 \\
    RIMPA0093 & 699887 & Guerrero & 26    & 0.076923077 & 0.923076923 \\
    RIMPA0094 & 699888 & Guerrero & 2     & 0     & 1 \\
    RIMPA0095 & 699889 & Guerrero & 4     & 0     & 1 \\
    RIMPA0096 & 699890 & Guerrero & 26    & 0.038461538 & 0.961538462 \\
    RIMPA0097 & 699891 & Guerrero & 6     & 0     & 1 \\
    RIMPA0098 & 699892 & Guerrero & 4     & 0     & 1 \\
    RIMPA0099 & 699893 & Guerrero & 4     & 0     & 1 \\
    RIMPA0100 & 699894 & Guerrero & 6     & 0     & 1 \\
    RIMPA0101 & 699895 & Guerrero & 2     & 0     & 1 \\
    RIMPA0103 & 699897 & Guerrero & 2     & 0     & 1 \\
    RIMPA0104 & 699898 & Guerrero & 22    & 0.090909091 & 0.909090909 \\
    RIMPA0105 & 699899 & Guerrero & 6     & 0     & 1 \\
    RIMPA0106 & 699900 & Guerrero & 6     & 0.333333333 & 0.666666667 \\
    RIMPA0107 & 699901 & Guerrero & 4     & 0     & 1 \\
    RIMPA0108 & 699902 & Guerrero & 6     & 0     & 1 \\
    RIMPA0109 & 699903 & Michoacan & 4     & 0.25  & 0.75 \\
    RIMPA0110 & 699904 & Michoacan & 2     & 0     & 1 \\
    RIMPA0111 & 699905 & Michoacan & 4     & 0     & 1 \\
    RIMPA0112 & 699906 & Michoacan & 4     & 0.25  & 0.75 \\
    RIMPA0114 & 699908 & Michoacan & 6     & 0.166666667 & 0.833333333 \\
    RIMPA0116 & 699910 & Mexico & 2     & 0     & 1 \\
    RIMPA0117 & 699911 & Mexico & 4     & 0     & 1 \\
    RIMPA0118 & 699912 & Mexico & 6     & 0.166666667 & 0.833333333 \\
    RIMPA0119 & 699913 & Mexico & 2     & 0     & 1 \\
    RIMPA0120 & 699914 & Mexico & 1     & 1     & 0 \\
    RIMPA0121 & 699915 & Mexico & 2     & 0     & 1 \\
    RIMPA0128 & 699922 & Mexico & 2     & 0.5   & 0.5 \\
    RIMPA0129 & 699923 & Michoacan & 2     & 0.5   & 0.5 \\
    RIMPA0135 & 699929 & Nayarit & 24    & 0     & 1 \\
    RIMPA0138 & 699932 & Jalisco & 2     & 0.5   & 0.5 \\
    RIMPA0139 & 699933 & Jalisco & 1     & 1     & 0 \\
    RIMPA0142 & 699936 & Colima & 18    & 0.444444444 & 0.555555556 \\
    RIMPA0144 & 699938 & Jalisco & 2     & 1     & 0 \\
    RIMPA0145 & 699939 & Michoacan & 1     & 1     & 0 \\
    RIMPA0147 & 699941 & Jalisco & 1     & 1     & 0 \\
    RIMPA0155 & N/A   & Jalisco & 73    & 0.01369863 & 0.98630137 \\
    RIMPA0156 & N/A   & Jalisco & 20    & 0     & 1 \\
    RIMPA0157 & N/A   & Jalisco & 58    & 0.344827586 & 0.655172414 \\
    RIMPA0158 & N/A   & Jalisco & 64    & 0.53125 & 0.46875 \\
    RIMPA0159 & N/A   & Jalisco & 26    & 0     & 1 \\
    RIMPA0162 & 21785 & N/A   & 4     & 0     & 1 \\
\end{longtable}

@@

% Table S2. Mays sampling
\begin{table}[htbp]
\rowcolors{2}{gray!25}{white}
  \centering

@@

\end{document}
